Early Observations of the Type Ia Supernova \abc:\\ \textbf{a Case of Interaction with Nearby, Unbound Material and/or} Strong Ejecta Mixing

### 2017-11-20 doc/ms.tex
Update figure widths to inches

In this paper, we report observations of an extraordinarily young SN Ia, \abc,
which was discovered by the intermediate Palomar Transient Factory (iPTF) on
2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$,
$\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a
$g_\mathrm{PTF}$-band magnitude of $21.31\pm0.27$ \citep{2016ATel.8907....1M}.
The transient is spatially coincident with a tidal tail of the galaxy
NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected
to a limit of $g_\mathrm{PTF}=22.1$\,mag on April $2.42$, less than 1\,d prior
to discovery, and rose by $\sim$2\,mag in the 24\,hr following its initial
detection. Our spectroscopic follow-up campaign classified \abc\ as a normal
SN Ia \citep{2016ATel.8909....1C}. Our observations and analysis show that the
early evolution of \abc\ exhibited several distinct properties relative to
SN\,2011fe. We interpret those differences as arising from either strong
$^{56}$Ni mixing or ejecta interaction with \textbf{nearby, unbound} material,
or a combination of the two. Alongside this paper, we have released our open
source analysis and all of the data utilized in this study. These are
available online at \texttt{GitHub}
\url{https://github.com/adamamiller/iPTF16abc}.

@@

\begin{figure}[htb] 
    \centering
    \includegraphics[width=0.48\textwidth]{logLC_with_colors.pdf} 
    \caption{
    The $g$-band light curve of \abc. Observations from different telescopes
    are shown with different symbols. Time is measured in rest-frame days
    relative to $t_0$ (see \S\ref{sec:lc_fit}). Note that the horizontal axis
    is shown with a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \;
    \mathrm{d}$ and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$.
    \textbf{Vertical} black ticks show epochs of spectroscopic observations. }
    \label{fig:lightcurve} 
\end{figure}

@@

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=0.69\textwidth]{spectra.pdf}
  \caption{
  Observed spectral sequence of \abc. The spectra are normalized by their
  median flux between 6000 and 7000$\,\textrm{\AA}$. The phase of each
  spectrum relative to \textbf{the time of $B$-band maximum} is shown.
  Telluric absorption bands are grayed out. Line identifications are provided
  for the spectral features discussed in the text. For clarity,
  high-resolution spectra obtained with the VLT have been omitted (see
  \citealt{2017A&A...606A.111F} for a detailed discussion of these spectra).}
  \label{fig:spec_seq}
\end{figure*}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
  \caption{
  \textbf{Velocity evolution of \ion{Si}{2},
  $v_{\mathrm{Si\,II}\,\lambda6355}$, for \abc\ compared to the median
  evolution of the four spectroscopic subclasses defined in
  \citet{2006PASP..118..560B}, using data from \citet{2012AJ....143..126B}.
  Typical uncertainties for \abc\ are $\sim$1000\,km\,s$^{-1}$ before
  $T_{B,\mathrm{max}}$, when the \ion{Si}{2}$\,\lambda6355$ profile is shallow
  and the minimum of absorption is difficult to determine, and
  $\sim$300\,km\,s$^{-1}$ after $T_{B,\mathrm{max}}$. For the median curves,
  the typical scatter, determined via the interquartile range of the sample,
  is $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$. At early times,
  core-normal and broad-line SNe have significantly faster \ion{Si}{2} than
  \abc, while the declining trend of cool SNe does not match \abc.} }
  \label{fig:branch_vel}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.48\textwidth]{early_lc.pdf}
  \caption{
  Best-fit $f \propto t^\alpha$ model to describe the early flux from \abc\ in
  the $g_\mathrm{PTF}$ band. \textit{Top}: The relative flux,
  $f_{g_\mathrm{PTF}}$, shown as green circles, is measured via forced-PSF
  photometry. The model flux, adopting best-fit parameters $\alpha=0.98$ and
  $t_0=-17.91\,\textrm{d}$, is shown as a thick, dashed line. Also shown is
  the best-fit model after fixing $\alpha=2$ (thin, dash-dot line). The inset
  shows the joint distribution of $t_0$ and $\alpha$ for the best-fit
  power-law model. The solid contours represent the $68\%$ and $99.7\%$
  confidence levels. \textit{Bottom}: The observations and models following
  subtraction of the best-fit power-law model, $f_{\alpha = 0.98}$. The
  $t^{0.98}$ model provides a much better fit to the observations than the
  $t^2$ model.}
  \label{fig:early_lc_fit}
\end{figure}

@@

\begin{figure*}[!thb]
  \centering
  \includegraphics[width=0.48\textwidth]{Chi2.pdf}
  \includegraphics[width=0.48\textwidth]{VelocityPlot.pdf}
  \caption{
  Constraints on $t_\mathrm{exp}$ from the velocity evolution of \ion{Si}{2}.
  \textit{Left panel:} the dashed, solid and dash-dotted curves show $\chi^2$
  for fitting power laws with indices $-0.20$, $-0.22$ and $-0.24$,
  respectively. The blue vertical line and the orange shaded region indicate
  $t_0$ and its 95\% confidence interval from Section \ref{sec:lc_fit},
  respectively. \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
  velocities (blue circles) and the best-fit power-law model with an index of
  $-0.22$ (dashed line). \textbf{For comparison}, the measured velocities of
  \ion{C}{2}\,$\lambda\lambda$6580, 7234 are also shown. Typical uncertainties
  are smaller than the size of the points. \textit{Right inset}: Evolution of
  the pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and
  \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the $\sim$7\,d following 
  explosion.}
  \label{fig:velocity_t_exp}
\end{figure*}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.49\textwidth]{CarbonFeature.pdf}
  \caption{
  Evolution of the \ion{C}{2} features observed in the early spectra of \abc.
  The raw spectra are shown in orange, while the solid blue lines show the
  best-fit models (see text for further details). The dark grey vertical lines
  show the measured line centers, \textbf{and clearly show} the decline in the
  photosphere velocity in the $\sim$7~d after explosion (
  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d spectrum). The
  phase of each spectrum relative to $T_{B,\mathrm{max}}$ is labeled.
  }
  \label{fig:carbon}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{16abc_11fe_colors.pdf}
  \caption{$(B - V)_0$ color evolution of \abc\ (squares) 
    compared to SN\,2011fe (stars). The $B$ and $V$ photometry are calibrated
    on the Vega system, and have been corrected for extinction. The data for
    SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
  \label{fig:B-Vcolors}
\end{figure}

@@

\begin{figure}[!thb]
  \centering
  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
  \caption{Comparison of SN ejecta-companion interaction models 
  with early observations of \abc. $g_\mathrm{PTF}$ 
  detections and 3$\sigma$ upper limits are shown 
  as green circles and downward arrows, respectively. 
  \textit{Swift}/$UVW1$ observations are shown as magenta hexagons.
  The dashed, solid, and dash-dot lines show the expected flux 
  for companion-interaction models in the $g_\mathrm{PTF}$ (green) 
  and $UVW1$ (magenta) filters. The models have been adjusted to 
  account for the distance and reddening towards \abc. Each 
  model features a different companion semi-major axis, $a$, and 
  time of explosion, $t_\mathrm{exp}$, as labeled in the 
  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
  explain the early optical rise, they greatly 
  overpredict the UV flux. Models with $a \approx 10^{11} \, 
  \mathrm{cm}$ can explain the initial detection \abc, but they 
  fail to replicate the $\sim$2\,mag rise in the $\sim$24\,hr 
  after explosion.
  }
  \label{fig:SN-companion}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Noebauer.pdf}
  \caption{
  %
  \textbf{Comparison of the models from \citet{2017MNRAS.472.2787N} to the
  \abc\ $V$-band light curve (\textit{top}) and the $(B-V)_0$ color curve
  (\textit{bottom}). The light curve has been corrected for the distance
  modulus to \abc\ (\S\ref{sec:host}), while both the light curve and color
  curve have been corrected for reddening. To guide the eye,
  $g_\mathrm{PTF}$ observations are shown, though we caution
  that \abc\ may exhibit significant color evolution at this phase in which
  case $g_\mathrm{PTF}$ would be a poor proxy for $V$. Each model light curve
  is translated to match the LCO observations $\sim$1.7\,d after $t_0$ given
  the uncertain time of explosion. Translational offsets are listed in the
  bottom panel legend, which shows the models in order of decreasing
  $^{56}$Ni from top to bottom, then left to right. The inset in
  the top panel shows the residuals relative to the W7 model.} }
  %
  \label{fig:noebauer} 
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Dessart.pdf}
  \caption{
  %
  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the $g$-band light
  curve and the DD and PDD models from \citet{2014MNRAS.441..532D}. The bottom
  panel legend lists the models in order of decreasing $M_\mathrm{Ni}$ from
  top to bottom. DD models (labeled as DDC to match the nomenclature of
  \citealt{2014MNRAS.441..532D}) are shown as dash-dot lines, while PDD models
  (labeled as PDDEL) are shown as dashed lines. The inset in the top panel
  shows the residuals relative to the PDDEL7n model. The PDD models provide a
  better match to the observations.} }
  %
  \label{fig:dessart} 
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=0.48\textwidth]{compare_Piro.pdf}
  \caption{
  %
  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the $g$-band light
  curve and models from \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni
  mixing in the SN ejecta increases from the short-dash, light lines to the
  long-dash, dark lines. Unlike Figure~\ref{fig:dessart}, each model features
  the same $M_\mathrm{Ni}$, while the model names reflect the boxcar widths
  used to approximate the effects of mixing in the ejecta (see
  \citealt{2016ApJ...826...96P}). The top panel inset shows the residuals
  relative to the $0.25\,M_\odot$ model. The observations are best matched by
  the $0.25\,M_\odot$ model, i.e. the model with the most significant mixing.}}
  %
  \label{fig:piro}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.48\textwidth]{lightcurve.pdf}
  \caption{
  %
  UV, optical, and NIR light curves for \abc. \textit{Top}: $BVgri$ light
  curves from the P48, P60, LCO-1m, and \textit{Swift} telescopes. The solid
  lines represent the best-fit model from SALT2 (see
  \S\ref{sec:classification}). \textit{Bottom}: UV and NIR light curves from
  the \textit{Swift} and SPM-1.5m telescopes, respectively. For both panels
  each light curve is represented with a different color, while the different
  symbols correspond to different instruments, as detailed in the legends. The
  legends also list offsets applied to each light curve. Photometry is shown
  in the AB mag system, with the exception of the $BV$ bands, which are shown
  in the Vega system. These \textbf{light curves have} not been corrected for
  line-of-sight extinction.}
  %
  \label{fig:ugly_LC}
\end{figure}

>>>>

In this paper, we report observations of an extraordinarily young SN Ia, \abc,
which was discovered by the intermediate Palomar Transient Factory (iPTF) on
2016 April $3.36$ UTC at $\textrm{R.A.}=13^h34^m45.49^s$,
$\textrm{Dec.}=+13\degr51\arcmin14\farcs3$ (J2000) with a
$g_\mathrm{PTF}$-band magnitude of $21.44\pm0.25$ \citep{2016ATel.8907....1M}.
The transient is spatially coincident with a tidal tail of the galaxy
NGC\,5221, which lies at a distance of $\sim$100\,Mpc. \abc\ is not detected
to a 5-$\sigma$ limit of $g_\mathrm{PTF}=21.9$\,mag on April $2.42$, less than
1\,d prior to discovery, and rose by $\sim$2\,mag in the 24\,hr following its
initial detection. Our spectroscopic follow-up campaign classified \abc\ as a
normal SN Ia \citep{2016ATel.8909....1C}. Our observations and analysis show
that the early evolution of \abc\ exhibited several distinct properties
relative to SN\,2011fe. We interpret those differences as arising from either
strong $^{56}$Ni mixing or ejecta interaction with \textbf{nearby, unbound}
material, or a combination of the two. Alongside this paper, we have released
our open source analysis and all of the data utilized in this study. These are
available online at \texttt{GitHub}
\url{https://github.com/adamamiller/iPTF16abc}.

@@

\begin{figure}[htb] 
    \centering
    \includegraphics[width=3.35in]{logLC_with_colors.pdf} 
    \caption{
    %
    The $g$-band light curve of \abc, with 5-$\sigma$ upper limits shown as
    downward arrows. Observations from different telescopes are shown with
    different symbols. The lower axis shows time measured in rest-frame days
    relative to $t_0$ (see \S\ref{sec:lc_fit}), while the upper axis shows
    time relative to $B$-band maximum. Note that the horizontal axis is shown
    with a linear scale for $-2 \; \mathrm{d} \le t - t_0 \le 3 \; \mathrm{d}$
    and a $\log$ scale for $t - t_0 > 3 \; \mathrm{d}$. \textbf{Vertical}
    black ticks show epochs of spectroscopic observations. }
% 
    \label{fig:lightcurve} 
\end{figure}

@@

\begin{figure*}[!htb]
  \centering
  \includegraphics[width=5.5in]{spectra.pdf}
  \caption{
  Observed spectral sequence of \abc. The spectra are normalized by their
  median flux between 6000 and 7000$\,\textrm{\AA}$. The phase of each
  spectrum relative to \textbf{the time of $B$-band maximum} is shown.
  Telluric absorption bands are grayed out. Line identifications are provided
  for the spectral features discussed in the text. For clarity,
  high-resolution spectra obtained with the VLT have been omitted (see
  \citealt{2017A&A...606A.111F} for a detailed discussion of these spectra).}
  \label{fig:spec_seq}
\end{figure*}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=3.35in]{Branch_vel_evol.pdf}
  \caption{
  \textbf{Velocity evolution of \ion{Si}{2},
  $v_{\mathrm{Si\,II}\,\lambda6355}$, for \abc\ compared to the median
  evolution of the four spectroscopic subclasses defined in
  \citet{2006PASP..118..560B}, using data from \citet{2012AJ....143..126B}.
  Typical uncertainties for \abc\ are $\sim$1000\,km\,s$^{-1}$ before
  $T_{B,\mathrm{max}}$, when the \ion{Si}{2}$\,\lambda6355$ profile is shallow
  and the minimum of absorption is difficult to determine, and
  $\sim$300\,km\,s$^{-1}$ after $T_{B,\mathrm{max}}$. For the median curves,
  the typical scatter, determined via the interquartile range of the sample,
  is $\sim$700\,km\,s$^{-1}$, around $T_{B,\mathrm{max}}$. At early times,
  core-normal and broad-line SNe have significantly faster \ion{Si}{2} than
  \abc, while the declining trend of cool SNe does not match \abc.} }
  \label{fig:branch_vel}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=3.35in]{early_lc.pdf}
  \caption{
  Best-fit $f \propto t^\alpha$ model to describe the early flux from \abc\ in
  the $g_\mathrm{PTF}$ band. \textit{Top}: The relative flux,
  $f_{g_\mathrm{PTF}}$, shown as green circles, is measured via forced-PSF
  photometry. The model flux, adopting best-fit parameters $\alpha=0.98$ and
  $t_0=-17.91\,\textrm{d}$, is shown as a thick, dashed line. Also shown is
  the best-fit model after fixing $\alpha=2$ (thin, dash-dot line). The inset
  shows the joint distribution of $t_0$ and $\alpha$ for the best-fit
  power-law model. The solid contours represent the $68\%$ and $99.7\%$
  confidence levels. \textit{Bottom}: The observations and models following
  subtraction of the best-fit power-law model, $f_{\alpha = 0.98}$. The
  $t^{0.98}$ model provides a much better fit to the observations than the
  $t^2$ model.}
  \label{fig:early_lc_fit}
\end{figure}

@@

\begin{figure*}[!thb]
  \centering
  \includegraphics[width=3.35in]{Chi2.pdf}
  \includegraphics[width=3.35in]{VelocityPlot.pdf}
  \caption{
  Constraints on $t_\mathrm{exp}$ from the velocity evolution of \ion{Si}{2}.
  \textit{Left panel:} the dashed, solid and dash-dotted curves show $\chi^2$
  for fitting power laws with indices $-0.20$, $-0.22$ and $-0.24$,
  respectively. The blue vertical line and the orange shaded region indicate
  $t_0$ and its 95\% confidence interval from Section \ref{sec:lc_fit},
  respectively. \textit{Right panel:} Observed \ion{Si}{2}\,$\lambda$6355
  velocities (blue circles) and the best-fit power-law model with an index of
  $-0.22$ (dashed line). \textbf{For comparison}, the measured velocities of
  \ion{C}{2}\,$\lambda\lambda$6580, 7234 are also shown. Typical uncertainties
  are smaller than the size of the points. \textit{Right inset}: Evolution of
  the pseudo-equivalent width of \ion{Si}{2}\,$\lambda$6355, and
  \ion{C}{2}\,$\lambda\lambda$6580, 7234 in the $\sim$7\,d following 
  explosion.}
  \label{fig:velocity_t_exp}
\end{figure*}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=3.35in]{CarbonFeature.pdf}
  \caption{
  Evolution of the \ion{C}{2} features observed in the early spectra of \abc.
  The raw spectra are shown in orange, while the solid blue lines show the
  best-fit models (see text for further details). The dark grey vertical lines
  show the measured line centers, \textbf{and clearly show} the decline in the
  photosphere velocity in the $\sim$7~d after explosion (
  \ion{C}{2}\,$\lambda$7234 is not detected in the $-10.9$\,d spectrum). The
  phase of each spectrum relative to $T_{B,\mathrm{max}}$ is labeled.
  }
  \label{fig:carbon}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=3.35in]{16abc_11fe_colors.pdf}
  \caption{$(B - V)_0$ color evolution of \abc\ (squares) 
    compared to SN\,2011fe (stars). The $B$ and $V$ photometry are calibrated
    on the Vega system, and have been corrected for extinction. The data for
    SN\,2011fe are from \citet{2016ApJ...820...67Z}.}
  \label{fig:B-Vcolors}
\end{figure}

@@

\begin{figure}[!thb]
  \centering
  \includegraphics[width=3.35in]{companion_lc.pdf}
  \caption{Comparison of SN ejecta-companion interaction models 
  with early observations of \abc. $g_\mathrm{PTF}$ 
  detections and 3$\sigma$ upper limits are shown 
  as green circles and downward arrows, respectively. 
  \textit{Swift}/$UVW1$ observations are shown as magenta hexagons.
  The dashed, solid, and dash-dot lines show the expected flux 
  for companion-interaction models in the $g_\mathrm{PTF}$ (green) 
  and $UVW1$ (magenta) filters. The models have been adjusted to 
  account for the distance and reddening towards \abc. Each 
  model features a different companion semi-major axis, $a$, and 
  time of explosion, $t_\mathrm{exp}$, as labeled in the 
  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
  explain the early optical rise, they greatly 
  overpredict the UV flux. Models with $a \approx 10^{11} \, 
  \mathrm{cm}$ can explain the initial detection \abc, but they 
  fail to replicate the $\sim$2\,mag rise in the $\sim$24\,hr 
  after explosion.
  }
  \label{fig:SN-companion}
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=3.35in]{compare_Noebauer.pdf}
  \caption{
  %
  \textbf{Comparison of the models from \citet{2017MNRAS.472.2787N} to the
  \abc\ $V$-band light curve (\textit{top}) and the $(B-V)_0$ color curve
  (\textit{bottom}). The light curve has been corrected for the distance
  modulus to \abc\ (\S\ref{sec:host}), while both the light curve and color
  curve have been corrected for reddening. To guide the eye,
  $g_\mathrm{PTF}$ observations are shown, though we caution
  that \abc\ may exhibit significant color evolution at this phase in which
  case $g_\mathrm{PTF}$ would be a poor proxy for $V$. Each model light curve
  is translated to match the LCO observations $\sim$1.7\,d after $t_0$ given
  the uncertain time of explosion. Translational offsets are listed in the
  bottom panel legend, which shows the models in order of decreasing
  $^{56}$Ni from top to bottom, then left to right. The inset in
  the top panel shows the residuals relative to the W7 model.} }
  %
  \label{fig:noebauer} 
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=3.35in]{compare_Dessart.pdf}
  \caption{
  %
  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the $g$-band light
  curve and the DD and PDD models from \citet{2014MNRAS.441..532D}. The bottom
  panel legend lists the models in order of decreasing $M_\mathrm{Ni}$ from
  top to bottom. DD models (labeled as DDC to match the nomenclature of
  \citealt{2014MNRAS.441..532D}) are shown as dash-dot lines, while PDD models
  (labeled as PDDEL) are shown as dashed lines. The inset in the top panel
  shows the residuals relative to the PDDEL7n model. The PDD models provide a
  better match to the observations.} }
  %
  \label{fig:dessart} 
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=3.35in]{compare_Piro.pdf}
  \caption{
  %
  \textbf{Same as Figure~\ref{fig:noebauer}, featuring the $g$-band light
  curve and models from \citet{2016ApJ...826...96P}. The amount of $^{56}$Ni
  mixing in the SN ejecta increases from the short-dash, light lines to the
  long-dash, dark lines. Unlike Figure~\ref{fig:dessart}, each model features
  the same $M_\mathrm{Ni}$, while the model names reflect the boxcar widths
  used to approximate the effects of mixing in the ejecta (see
  \citealt{2016ApJ...826...96P}). The top panel inset shows the residuals
  relative to the $0.25\,M_\odot$ model. The observations are best matched by
  the $0.25\,M_\odot$ model, i.e. the model with the most significant mixing.}}
  %
  \label{fig:piro}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \includegraphics[width=3.35in]{lightcurve.pdf}
  \caption{
  %
  UV, optical, and NIR light curves for \abc. \textit{Top}: $BVgri$ light
  curves from the P48, P60, LCO-1m, and \textit{Swift} telescopes. The solid
  lines represent the best-fit model from SALT2 (see
  \S\ref{sec:classification}). \textit{Bottom}: UV and NIR light curves from
  the \textit{Swift} and SPM-1.5m telescopes, respectively. For both panels
  each light curve is represented with a different color, while the different
  symbols correspond to different instruments, as detailed in the legends. The
  legends also list offsets applied to each light curve. Photometry is shown
  in the AB mag system, with the exception of the $BV$ bands, which are shown
  in the Vega system. These \textbf{light curves have} not been corrected for
  line-of-sight extinction.}
  %
  \label{fig:ugly_LC}
\end{figure}
